Gravitational Lens Modeling in a Citizen Science Context

### 2014-08-05 text/ms.tex

\begin{figure}
  \centering
    \includegraphics[width=0.90\linewidth]{fig/screenshot}
  \caption{\phil{Screen grab of \spl in action. A \sw image has been loaded
  in, re-centred and zoomed, and 5 images and associated time delay
  surface `spaghetti'' contours suggested, using the marking tools
  associated with the buttons along the top of the panel. The mass
  model is optimized server-side 
  when the right-most button is pressed.}}
  \label{fig:screenshot}
\end{figure}

@@

Each of Figures \ref{fig:6941}--\ref{fig:7022} figures has the
following layout.
$$ \begin{matrix}
\hbox{marked-up image} \qquad &\hbox{model synthetic image} \\
t(x,y)                        &\hbox{model } t(x,y) \\
\kappa(x,y)                   &\hbox{model } \kappa(x,y)
\end{matrix} $$
The marked-up image is a zoom of the lensed image on \sw,
marked up with one or more spaghetti contours; this is the modeller's
input to \spl.  The three panels on the right show the graphical
output returned to the modeller by \spl, listed as (i), (ii), (iii) in
\secref{SpaghettiLens}.  These derive from the mean of an ensemble of
200 models generated by \spl. The model synthetic image is too crude
to be useful, because there is no fitting for the source light
distribution, as already noted in \secref{diag}.  The quality of the
synthetic images can be improved by interpolation, but as this feature
was not available during the modelling challenge, we do not show the
improved versions here.

@@

% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
% THIS PARAGRAPH TO BE REMOVED WHEN THE FIGURES ARE FIXED!
%
In these figures, the scales and alignments in the six panels are not
completely consistent: the three panels on the right have the same
coordinates; the middle-left and lower-left panels are consistent with
each other, but only approximately aligned with the right column,
because the latter are affected by errors in mouse placements; the
upper-left panel is zoomed out slightly, to accommodate the full
markup.  For qualitative features, which is all that
Figures~\ref{fig:6941}--\ref{fig:7022} try to convey, the slightly
varying scales and alignments are harmless.
% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

>>>>

\begin{figure}
  \centering
    \includegraphics[width=0.90\linewidth]{fig/screenshot}
  \caption{Screen grab of \spl in action. A \sw image has been loaded
    in, re-centred and zoomed, and 5 images and associated time delay
    surface ``spaghetti'' contours suggested, using the marking tools
    associated with the buttons along the top of the panel. The mass
    model is optimized server-side when the right-most button is
    pressed.}
  \label{fig:screenshot}
\end{figure}

@@

@@

Each of Figures \ref{fig:6941}--\ref{fig:7022} figures has the
following layout.
$$ \begin{matrix}
\hbox{marked-up image} \qquad &\hbox{model synthetic image} \\
t(x,y)                        &\hbox{model } t(x,y) \\
\kappa(x,y)                   &\hbox{model } \kappa(x,y)
\end{matrix} $$

% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
% THIS PARAGRAPH TO BE REMOVED WHEN THE FIGURES ARE FIXED!
%
% In these figures, the scales and alignments in the six panels are not
% completely consistent: the three panels on the right have the same
% coordinates; the middle-left and lower-left panels are consistent with
% each other, but only approximately aligned with the right column,
% because the latter are affected by errors in mouse placements; the
% upper-left panel is zoomed out slightly, to accommodate the full
% markup.  For qualitative features, which is all that
% Figures~\ref{fig:6941}--\ref{fig:7022} try to convey, the slightly
% varying scales and alignments are harmless.
% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
